\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-10-10 draft.tex
rough in proofs for tau^ad; proof tad_dir and all but last line of tad_indir

@@

\vskip.4in
\noindent \textbf{\hypertarget{Pr_lobby}{Proof of Lemma~\ref{res:lobby}}}:\\
Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
  \[
		\frac{\partial e}{\partial \tau^a} = - \frac{\frac{\partial FOC_L}{\partial \tau^a}}{\frac{\partial FOC_L}{\partial e}} = \frac{ \frac{\partial r}{\partial e} \frac{\partial \pi(\bta)}{\partial \tau^a} - \frac{\partial^2 r}{\partial e \partial \tau^a} \left[ \pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
	\]
Beginning with the denominator: $\tad > \tau^a$ and $\pi(\cdot)$ is increasing in $\tau$ so the expression is brackets is positive. $\frac{\partial^2 r}{\partial e^2}$ is negative by Result~\ref{res:bincC}, so the denominator is negative.

Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive and $\frac{\partial \pi(\bta)}{\partial \tau^a}$ is positive by construction so the first term is positive.

@@

Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive and $\frac{\partial \pi(\bta)}{\partial \tau^a}$ is positive by construction so the first term is positive.

@@

>>>>

\subsection{Antidumping Duties}
\label{sec:tad}

\begin{lemma}
  The direct effect of an increase in the antidumping duty on the probability the government renews the antidumping duties is negative. \hyperlink{Pr_tad_dir}{Proof}
  \label{res:tad_dir}
\end{lemma}

\begin{lemma}
  Lobbying effort is weakly increasing in the antidumping duties. \hyperlink{Pr_tad_indir}{Proof}
  \label{res:tad_indir}
\end{lemma}

\begin{result}
	The total probability that the antidumping duties will be renewed is increasing in level of the antidumping duties $\tad$. (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \pi} \geq 0$). \hyperlink{Pr_tad_total}{Proof}
	\label{res:tad_total}
\end{result}

@@

\vskip.4in
\noindent \textbf{\hypertarget{Pr_lobby}{Proof of Lemma~\ref{res:lobby}}}:\\
Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
  \[
		\frac{\partial e}{\partial \tau^a} = - \frac{\frac{\partial FOC_L}{\partial \tau^a}}{\frac{\partial FOC_L}{\partial e}} = \frac{ \frac{\partial r}{\partial e} \frac{\partial \pi(\tau^a)}{\partial \tau^a} - \frac{\partial^2 r}{\partial e \partial \tau^a} \left[ \pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
	\]
Beginning with the denominator: $\tad > \tau^a$ and $\pi(\cdot)$ is increasing in $\tau$ so the expression is brackets is positive. $\frac{\partial^2 r}{\partial e^2}$ is negative by Result~\ref{res:bincC}, so the denominator is negative.

Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive and $\frac{\partial \pi(\tau^a)}{\partial \tau^a}$ is positive by construction so the first term is positive.

@@

Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive and $\frac{\partial \pi(\tau^a)}{\partial \tau^a}$ is positive by construction so the first term is positive.

@@

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_tad_dir}{Proof of Lemma~\ref{res:tad_dir}}}: \\
The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tad$; to show that the renewal probability is decreasing in $\tad$, I must demonstrate that this derivative is positive. Again labeling the numerator of that expression $Z(\bta,\tad)$, the derivative of this quantity with respect to $\tad$ is

\begin{equation}
  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial \mathit{CS}_X(\tad)}{\partial \tad} + \frac{\partial \pi_X(\tad)}{\partial \tad} + \frac{\partial \mathit{TR}(\tad)}{\partial \tad}\right) + Z(\bta,\tad) \frac{\partial \pi_X(\tad)}{\partial \tad}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:tad}
\end{equation}

\noindent $\left(\pi_X(\tau^a) - \pi_X(\tad)\right)$ is always negative. Because the optimal unilateral tariff for large welfare-maximizing governments is positive (call it $\tau^O$), $\left(\frac{\partial \mathit{CS}_X(\tad)}{\partial \tad} + \frac{\partial \pi_X(\tad)}{\partial \tad} + \frac{\partial \mathit{TR}(\tad)}{\partial \tad}\right)$ is increasing up to $\tau^O$ and decreasing above it. Thus the first summand is increasing up until $\tau^O$ and decreasing thereafter. Note it seems unreasonable for $\tad$ to be smaller than $\tau^O$ but this can be proved for the general case so we will not assume it.

$Z(\bta,\tad)$ is also always positive on $[0,\tau^O]$ since $\tad > \tau^a$ and on this range $\tad$ is closer to the optimum. Profits are increasing in $\tad$, so the second summand is positive on $[0,\tau^O]$. With a positive denominator, we thus have that the entire express is positive on $[0,\tau^O]$.

It is also positive for all tariffs larger than $\tau^O$. To see this, add $\left(\tilde{\Gamma} - 1 \right) \frac{\partial \pi_X(\tad)}{\partial \tad} \left(\pi_X(\tau^a) - \pi_X(\tad)\right)$ to the first summand and subtract it from the second. For any particular value of $\tilde{\tau}^{ad}$, one can choose the $\tilde{\Gamma}$ weight that would make $\tilde{\tau}^{ad}$ the preferred unilateral tariff; this makes the derivative in the first summand zero. Having subtracted the same quantity from the second summand modifies the welfare difference in the second summand to be maximized at $\tilde{\tau}^{ad}$ so that this term is always positive. Since the denominator is a squared term of a strictly negative quantity, the expression in Equation~\ref{appex:tad} is positive for all $\tau^{ad}$.  $\hfill\blacksquare$

\vskip.4in
\noindent \textbf{\hypertarget{Pr_tad_indir}{Proof of Lemma~\ref{res:tad_indir}}}:\\
Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
  \[
		\frac{\partial e}{\partial \tad} = - \frac{\frac{\partial FOC_L}{\partial \tad}}{\frac{\partial FOC_L}{\partial e}} =
		- \frac{ \frac{\partial r}{\partial e} \frac{\partial \pi(\tad)}{\partial \tad} + \frac{\partial^2 r}{\partial e \partial \tad} \left[ \pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
	\]
The denominator is again negative.

Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive and $\frac{\partial \pi(\tad)}{\partial \tad}$ is positive by construction so the first term is positive.

We can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial  \tad} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tad} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \tad} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \tad}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.

Then $\frac{\partial^2 r}{\partial e \partial \tad} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tad} \right) = 
	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \tad \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \tad} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tad} \frac{\partial f_\ga}{\partial e} $
where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$. The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$. Thus $\frac{\partial e}{\partial \tau^a} \leq 0$.  $\hfill\blacksquare$

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_tad_total}{Proof of Result~\ref{res:tad_total}}}: \\
$\frac{\partial R(\bta,\tad)}{\partial \ga(\cdot)} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \ga(\cdot)} + \frac{\partial r}{\partial \ga(\cdot)}$. $\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}. $\frac{\partial e}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_indir}. $\frac{\partial r}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_dir}. Thus the entire expression is non-negative. $\hfill\blacksquare$
